\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Alex Levi Usselman}}\\
	Medford, OR $\cdot$ svytry123@gmail.com $\cdot$ 5416210643\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Mitchell High School}\hfill Colorado Springs, CO\\
Air Force Junior Reserve Officer Training Corps \textit{GPA: 2.7} \hfill 2013 - 2014\\
\vspace{2mm}
\textbf{Homeschool}\hfill Medford, OR\\
High School Diploma Computer Science \textit{GPA: 3.1} \hfill 2014 - 2017\\
\vspace{2mm}

%==== Experience ====%
\header{Work Expierence}
\vspace{1mm}

\textbf{Lizarraga Landscaping} \hfill Medford, OR\\
\textit{Landscaper / Hardscaper} \hfill 2014 - 2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Landscape and manage private grounds.
	\item Lay concrete brick and, tile.
	\item Run irrigation and drip lines on customer gardens and, lawns.
	\item Trim and, maintain bushs, hedges, flowers, and trees.
\end{itemize}
\textbf{Personnel Source} \hfill Eagle Point, OR\\
\textit{City of Eagle Point Public Works Temp} \hfill March, 2017 - August, 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Maintain parks grass and, removal of trash from the grounds.
	\item Working in teams to excavate and, fix underground water mains.
	\item Properly setting up playground equipment.
	\item Driving, maintaining, and using; city vehicles and equipment.
\end{itemize}
\textbf{Bear Creek Lock and Safe} \hfill Medford, OR\\
\textit{Locksmith} \hfill March, 2018 - July, 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Rekeying and, masterkeying private and, commerical locks.
	\item Safely and, efficiently gaining entry into locked vehicles using lockout tools.
	\item Excelling in customer service; dealing with returns, soothing angry customers, and always keeping a polite, kind demeanor.
	\item Lockpicking and, gain of entry.
	\item Restocking, and shopkeeping.
	\item Possessing a Oregon Construction Contractors Board certification.
	\item Possessing a Locksmith License with the city.
\end{itemize}
\textbf{Don\textquotesingle{}s Lock} \hfill Medford, OR\\
\textit{Mobile Locksmith} \hfill July, 2019 - February, 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Driving and, maintaining a company vehicle.
	\item Responding to AAA (Triple A) calls at all times of the day during \textquotesingle{}On Call\textquotesingle{} days.
	\item Lockpicking and, gain of entry into customer houses during housecalls.
	\item Possessing a Locksmith License with the city.
	\item Possessing a Oregon Construction Contractors Board certification.
	\item Entrusted with a company gas card.
	\item Bill customers and, maintain invoices.
	\item Restocking of parts and, equipment.
\end{itemize}
\textbf{UpperCase Computers} \hfill Medford, OR\\
\textit{IT Technician} \hfill July, 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Mounting and, installation of hardware.
	\item Installation and, configuring IP cameras to NAS storage systems.
	\item Installation and, configuration of routers, switches, and POE systems.
	\item Helpdesk and, troubleshooting.
	\item Maintaining utmost customer service with residential customers and, commerical clients.
	\item Remote troubleshooting on customer computers.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Basic Knowledge of:  & HTML, CSS, Python, SQL                                                 \\
	Confident in use of: & Microsoft Office Suite, GSuite, Wordpress, Magix Video and Audio Suite \\
\end{tabular}
\vspace{2mm}





\ 
\end{document}